### 2018-08-03 Sections/cloud_quantum_computing.tex
Some stuff

@@

Each of these stages present their own technological challenges, sufficiently challenging that one might wish to outsource all three stages. However, suppose there is no single host on the network with the ability to perform all three, but rather there are three hosts ($B_1$, $B_2$ and $B_3$), each specialising in just one of those tasks. In this instance, it would be most resource savvy for the network to implement the pipeline \mbox{$A\to B_1\to B_2\to B_3\to A$}, without going back and forth to Alice after each step (\mbox{$A\to B_1\to A\to B_2 \to A\to B_3\to A$}). In fact, it may not even be technologically possible to implement back-and-forth to Alice if she has no capacity for handling quantum resources (i.e the \mbox{$A\leftrightarrow B$} stages are purely classical). An example of such a pipeline is shown in Fig.~\ref{fig:delegated}.

@@

\begin{figure}[!htb]
	\includegraphics[width=0.475\textwidth]{modules_physical}
	\caption{A possible physical realisation of commercially produced quantum modules. Each hosts a relatively small number of qubits. The nodes each have four optical interconnects, which are used to connect the modules via optical fibre. Entangling operations performed on photons shared via the interconnects create inter-module entanglement, yielding a virtual quantum computer with far more qubits.}\label{fig:modules_physical}
\end{figure}

>>>>

\dropcap{W}{e} begin by introducing the primitive building blocks for cloud quantum computing. These form the foundation for higher-level protocols to be discussed later in this part.

@@

Each of these stages present their own technological challenges, sufficiently challenging that one might wish to outsource all three stages. However, suppose there is no single host on the network with the ability to perform all three, but rather there are three hosts ($B_1$, $B_2$ and $B_3$), each specialising in just one of those tasks. In this instance, it would be most resource savvy for the network to implement the pipeline,
\begin{align}
	A\to B_1\to B_2\to B_3\to A,
\end{align}
without going back and forth to Alice after each step,
\begin{align}
	A\to B_1\to A\to B_2 \to A\to B_3\to A.
\end{align}
In fact, it may not even be technologically possible to implement back-and-forth to Alice if she has no capacity for handling quantum resources (i.e the \mbox{$A\leftrightarrow B$} stages are purely classical). An example of such a pipeline is shown in Fig.~\ref{fig:delegated}.

@@

\begin{figure}[!htb]
	\includegraphics[width=0.475\textwidth]{modules_physical}
	\caption{A possible physical realisation of commercially produced quantum modules, forming a \mbox{$2\times 3$} patchwork of cluster states. Each hosts a relatively small number of qubits. The nodes each have four optical interconnects, which are used to connect the modules via optical fibre. Entangling operations performed on photons shared via the interconnects create inter-module entanglement, yielding a virtual quantum computer with far more qubits.}\label{fig:modules_physical}
\end{figure}

### 2018-08-03 Sections/cryptowars.tex
Some stuff

Numerous key exchange protocols have been formulated, the best known being the Diffie-Hellman\index{Diffie-Hellman protocol} protocol, which has been widely adopted on the internet.

@@

@@

Having introduced the main classes of classical cryptographic protocols, we now turn our attention to their weaknesses and vulnerabilities.

@@

\subsection{Brute-force}\index{Brute-force attacks}\label{sec:brute_force_attack}

@@

\subsubsection{Quantum attacks}

@@

\paragraph{Brute-force}\index{Brute-force attacks}\label{sec:brute_force_attacks}

@@

\paragraph{Cryptanalysis}\index{Cryptanalysis}

@@

\paragraph{Integer factorisation}\index{Integer factorisation}

In the case of RSA public-key cryptography the attack is more direct -- with access to a scalable quantum computer, Shor's algorithm\index{Shor's algorithm} can be employed to efficiently factorise large integers, allowing private keys to be retrieved from public keys. Unlike the brute-force attacks, which yielded only a quadratic enhancement, Shor's algorithm is exponentially faster than the classical GNFS, requiring runtime of only,
\begin{align}
	O([\log n]^2[\log\log n][\log\log\log n]).
\end{align}
Compare this with Eq.~(\ref{eq:GNFS_scaling}).

@@

@@

>>>>

Numerous key exchange protocols have been formulated, the best known being the Diffie-Hellman\index{Diffie-Hellman protocol} protocol \cite{DiffieHellman}, which has been widely adopted on the internet.

@@

\dropcap{H}aving introduced the main classes of classical cryptographic protocols, we now turn our attention to their weaknesses and vulnerabilities, both against adversaries with classical or quantum computational resources.

@@

All known classical attacks against any respected classical cryptosystem involve tremendous computational resources. After all, were this not the case the cryptosystem would be considered weak and would never have become widely adopted in the first place!

@@

\subsubsection{Brute-force}\index{Brute-force attacks}\label{sec:brute_force_attack}

@@

\subsection{Quantum attacks}

Having established that classical attacks against strong classical cryptosystems are quite limited by their implausible computational requirements, what if our adversary now has quantum computational resources? Does this change the game?

@@

\subsubsection{Brute-force}\index{Brute-force attacks}\label{sec:brute_force_attacks}

@@

@@

In the case of RSA public-key cryptography the attack is more direct -- with access to a scalable quantum computer, Shor's algorithm\index{Shor's algorithm} can be employed to efficiently factorise large integers, allowing private keys to be retrieved from public keys. Unlike the brute-force attacks, which yielded only a quadratic enhancement, Shor's algorithm is exponentially faster than the classical GNFS, requiring runtime of only,
\begin{align}
	O([\log n]^2[\log\log n][\log\log\log n]).
\end{align}
Compare this with the classical case given in Eq.~(\ref{eq:GNFS_scaling}).

@@

\dropcap{A}s quantum physics can compromise some important aspects of classical cryptography, can it perhaps be similarly exploited to make new cryptosystems that are immune even to quantum adversaries? Thankfully the answer is yes... at least some of the time.

@@

\subsubsection{Public-key cryptography}

The BB84 protocol is used exclusively for private-key cryptography. For many applications (notably digital signatures and easy key exchange with unidentified parties), public-key cryptosystems would be highly desirable.

Are there any viable public-key quantum protocols that could fill the vacancy of the soon-to-be-compromised RSA? Unfortunately the answer is `not yet'. As appealing as it would be, and despite many highly intelligent people putting their minds to it, to-date no one has presented a viable public-key quantum cryptosystem.

This is problematic since when quantum computing becomes a reality it will immediately compromise the classical public-key cryptosystems we all rely on on a daily basis, and it would be highly desirable for a quantum replacement to fill its shoes.

### 2018-08-03 Sections/encrypted_cloud_quantum_computing.tex
Some stuff

\comment{Si-Hui, I need your help in filling all the gaps in this section!}

Extremely important to many high-performance data-processing applications is security, as proprietary or sensitive data may be being dealt with. To address this, there are two models for encrypted, outsourced quantum computation -- \textit{homomorphic encryption} \cite{???, gentry2009fully, van2010fully}\index{Homomorphic encryption} and \textit{blind quantum computation}\index{Blind quantum computation} \cite{???, bib:blind2, bib:blind3, bib:blind1, PhysRevLett.108.200502, bib:Morimae3486, bib:Morimae5460, bib:Morimae3966}.

@@

\subsection{Digital signature}

>>>>

\dropcap{E}{xtremely} important to many high-performance data-processing applications is security, as proprietary or sensitive data may be being dealt with. To address this, there are two models for encrypted, outsourced quantum computation -- \textit{homomorphic encryption} \cite{???, gentry2009fully, van2010fully}\index{Homomorphic encryption} and \textit{blind quantum computation}\index{Blind quantum computation} \cite{???, bib:blind2, bib:blind3, bib:blind1, PhysRevLett.108.200502, bib:Morimae3486, bib:Morimae5460, bib:Morimae3966}.

@@

\subsection{Digital signatures}

### 2018-08-03 Sections/models_for_quantum_computation.tex
Some stuff

@@

As we have a heavy focus on applications to quantum computing, we begin by reviewing the models for quantum computation that we will refer to throughout this work.

>>>>

\dropcap{S}{ince} quantum computing is perhaps the most exciting of the emerging quantum technologies, which we treat as the foremost application for the quantum internet, we now introduce quantum computing, covering models and physical implementations for realising it, and some of its well-known algorithmic applications.

@@

\dropcap{W}{e} begin by reviewing the models for quantum computation that we will refer to throughout this work.
